---
title: "Spatial Analysis Results"
output: pdf_document
date: '2022-08-25'
---

Associated RData file (spatial_results.RData) can be downloaded at: https://mega.nz/folder/yBpA0IpA#jUZw1qrXeGQioN3bImE-Wg  

## Models 1a-1c: 77 timepoints

* Model 1: Baseline intensity (assumed different) for each location plus two linear time components, beginning on respective intervention dates (school closure and state mandated stay-at-home-order)

\setlength{\leftskip}{1cm}

a: Contact intensity between each pair of state borders is assumed to be different (termed distance model)  
b: Contact intensity between each pair of state borders is assumed to be the same (CAR model)  
c: Contact intensity between each pair of state borders is assumed to be different; the number of travelers between two locations (flow) increases with the locations' populations while decreases with the distance between them (gravity model)

\setlength{\leftskip}{0cm}

## Models 2a-2c: 184 timepoints

* Model 2: Baseline intensity (assumed different) for each location plus two linear time components, beginning on respective intervention dates (school closure and state mandated stay-at-home-order) and temporal basis splines of 3 degrees of freedom

\setlength{\leftskip}{1cm}

a-c: Same as above

 \setlength{\leftskip}{0cm}

## Model 3: 153 fitted timepoints, 297 missing/predicted timepoints (total: 450 timepoints)

* Model 3: Baseline intensity (assumed different) for each location, a temporal trigonometric term, the proportion of population vaccinated (at least one vaccine shot) and proportion fully vaccinated (all doses prescribed by the initial vaccination protocol) as recorded on 01/06/2021


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(ABSEIR)
library(forestmangr)
```

```{r}
load("./results.RData")
```



```{r}
plotPosteriorPredictive_firstwave(result1a, "Model 1a: Posterior Distribution")
plotPosteriorPredictive_firstwave(simulations1a, "Model 1a: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstwave(result1a_basic,"Model 1a (Basic ABC): Posterior Distribution")
plotPosteriorPredictive_firstwave(result1a_basic,"Model 1a (Basic ABC): Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstwave(result1a_weibull,"Model 1a (Weibull Distribution): Posterior Distribution")
plotPosteriorPredictive_firstwave(simulations1a_weibull,"Model 1a (Weibull Distribution): Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstwave(result1b, "Model 1b: Posterior Distribution")
plotPosteriorPredictive_firstwave(simulations1b, "Model 1b: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstwave(result1c, "Model 1c: Posterior Distribution")
plotPosteriorPredictive_firstwave(simulations1c, "Model 1c: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_compare_dm(result1a,result1b, result1c, "Model 1a vs Model 1b vs Model 1c: Posterior Distribution")
plotPosteriorPredictive_compare_dm(simulations1a,simulations1b, simulations1c, "Model 1a vs Model 1b vs Model 1c: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_compare_t1_alg(result1a,result1a_weibull,result1a_basic,result1a_basic_wei, "Model 1a: Posterior Distribution")
plotPosteriorPredictive_compare_t1_alg(simulations1a,simulations1a_weibull,simulations1a_basic,simulations1a_basic_wei, "Model 1a: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2a, "Model 2a: Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2a, "Model 2a: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2a_basic,"Model 2a (Basic ABC): Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2a_basic,"Model 2a (Basic ABC): Posterior Predictive Distribution")

# basic algorithm performs very poorly compared to SMC-ABC...we know that this happens when prior info is diffuse with regards to the posterior so in this case, especially because we are considering more than one location, it is likely that the provided prior means of the latent and infectious periods are diffuse to the actual lengths as seen in these particular three states.....notably, the basic algorithm performed rather well in the non-spatial analysis of florida implying that the provided priors were sufficient, however, here with different locations, this may not be the case. In reality, epidemic data is rarely truly ever described explicitly by the exponential distribution as it assumes a constant rate for the aforementioned periods; this is also why the Weibull distribution (which allows for a range of days rather than one constant value) is seen to be the better model for the longer timeline as confirmed via the Bayes factor evaluation.
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2a_weibull,"Model 2a (Weibull Distribution): Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2a_weibull,"Model 2a (Weibull Distribution): Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2a_weibull_basic,"Model 2a (Basic ABC, Weibull): Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2a_weibull_basic,"Model 2a (Basic ABC, Weibull): Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_compare_t2_alg(result2a,result2a_weibull,result2a_basic,result2a_weibull_basic, "Model 2a: Posterior Distribution")
plotPosteriorPredictive_compare_t2_alg(simulations2a,simulations2a_weibull,simulations2a_basic,simulations2a_weibull_basic, "Model 2a: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2b, "Model 2b: Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2b, "Model 2b: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive_firstandsecondwave(result2c, "Model 2c: Posterior Distribution")
plotPosteriorPredictive_firstandsecondwave(simulations2c, "Model 2c: Posterior Predictive Distribution")
```

```{r}
plotPosteriorPredictive(result4, vaccines_dates[-4], "Model 3: Posterior Distribution", lastTpt)
plotPosteriorPredictive(simulations4, vaccines_dates[-4], "Model 3: Posterior Predictive Distribution", lastTpt)
```

```{r}
plotPosteriorPredictive(result6, vaccines_dates[-4], "Model 3 (Weibull Distribution): Posterior Distribution", lastTpt)
plotPosteriorPredictive(simulations6, vaccines_dates[-4], "Model 3 (Weibull Distribution): Posterior Predictive Distribution", lastTpt)
```

```{r}
plotPosteriorPredictive_compare(result4,result6, vaccines_dates[-4], "Model 3: Posterior Distribution", lastTpt)
plotPosteriorPredictive_compare(simulations4,simulations6, vaccines_dates[-4], "Model 3: Posterior Predictive Distribution", lastTpt)
```



```{r}
beta_idx_1a <- grepl("Beta_SE", colnames(result1a$param.samples)) # use to get beta estimates/samples
eta_1a <- exposure_model_1$X %*% t(result1a$param.samples[,beta_idx_1a]) # get intensity matrix/time series (X(se) x Beta(se))
# dim: [T x p] * [n x p]^t where T = timepoints, n = no of samples and p = no of parameters
# after matrix multiplication: eta (intensity matrix) is T x n 

beta_idx_1b <- grepl("Beta_SE", colnames(result1b$param.samples)) # use to get beta estimates/samples
eta_1b <- exposure_model_1$X %*% t(result1b$param.samples[,beta_idx_1b]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_1c <- grepl("Beta_SE", colnames(result1c$param.samples)) # use to get beta estimates/samples
eta_1c <- exposure_model_1$X %*% t(result1c$param.samples[,beta_idx_1c]) # get intensity matrix/time series (X(se) x Beta(se))
 
 plot(apply(eta_1a, 1, mean), 
      type = 'l', 
      col="blue",
      main = 'Intensity Prediction',
      ylab = 'Intensity (Eta)',
      xlab = 'Epidemic Day',
      ylim = c(-10, max(eta_1a,eta_1b,eta_1c)*1.5))
 lines(apply(eta_1b, 1, mean), lty = 1, col = "red")
 lines(apply(eta_1c, 1, mean), lty = 1, col = "chartreuse2")
 abline(v=c(76,152), lty=c(2,2), lwd=c(2, 2), col="black")

 
 legend("bottomleft", legend = c("Model 1a", "Model 1b",
                               "Model 1c"), 
         lty = c(1,1,1), col = c("blue", "red", "chartreuse2"))


 
 # drives the I_star compartment
 # alabama has least epidemic intensity (which is true considering the amount of cases compared to fl and georgia), followed by florida and georgia
```



```{r}
beta_idx_1a_exp_SMC  <- grepl("Beta_SE", colnames(result1a$param.samples)) # use to get beta estimates/samples
eta_1a_exp_SMC<- exposure_model_1$X %*% t(result1a$param.samples[,beta_idx_1a_exp_SMC]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_1a_wei_SMC  <- grepl("Beta_SE", colnames(result1a_weibull$param.samples)) # use to get beta estimates/samples
eta_1a_wei_SMC<- exposure_model_1$X %*% t(result1a_weibull$param.samples[,beta_idx_1a_wei_SMC]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_1a_exp_basic  <- grepl("Beta_SE", colnames(result1a_basic$param.samples)) # use to get beta estimates/samples
eta_1a_exp_basic <- exposure_model_1$X %*% t(result1a_basic$param.samples[,beta_idx_1a_exp_basic]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_1a_wei_basic  <- grepl("Beta_SE", colnames(result1a_basic_wei$param.samples)) # use to get beta estimates/samples
eta_1a_wei_basic <- exposure_model_1$X %*% t(result1a_basic_wei$param.samples[,beta_idx_1a_wei_basic]) # get intensity matrix/time series (X(se) x Beta(se))
 
 plot(apply(eta_1a_exp_SMC, 1, mean), 
      type = 'l', 
      col="blue",
      main = 'Model 1a Intensity Prediction',
      ylab = 'Intensity (Eta)',
      xlab = 'Epidemic Day',
      ylim = c(-13, max(eta_1a_exp_SMC,eta_1a_wei_SMC,eta_1a_exp_basic,eta_1a_wei_basic)*1.5))
 lines(apply(eta_1a_wei_SMC, 1, mean), lty = 1, col = "red")
 lines(apply(eta_1a_exp_basic, 1, mean), lty = 1, col = "chartreuse2")
 lines(apply(eta_1a_wei_basic, 1, mean), lty = 1, col = "darkgoldenrod1")
 abline(v=c(77,153), lty=c(2,2), lwd=c(2, 2), col="black")

 
 
 
 legend("bottomleft", legend = c("Exponential (SMC)", "Weibull (SMC)",
                               "Exponential (Basic)", "Weibull (Basic)"), 
         lty = c(1,1,1,1), col = c("blue", "red", "chartreuse2", "darkgoldenrod1"))


# alabama has least epidemic intensity (which is true considering the amount of cases compared to fl and georgia), followed by florida and georgia
```

```{r}
beta_idx_2a_exp_SMC  <- grepl("Beta_SE", colnames(result2a$param.samples)) # use to get beta estimates/samples
eta_2a_exp_SMC<- exposure_model_2$X %*% t(result2a$param.samples[,beta_idx_2a_exp_SMC]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_2a_wei_SMC  <- grepl("Beta_SE", colnames(result2a_weibull$param.samples)) # use to get beta estimates/samples
eta_2a_wei_SMC<- exposure_model_2$X %*% t(result2a_weibull$param.samples[,beta_idx_2a_wei_SMC]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_2a_exp_basic  <- grepl("Beta_SE", colnames(result2a_basic$param.samples)) # use to get beta estimates/samples
eta_2a_exp_basic <- exposure_model_2$X %*% t(result2a_basic$param.samples[,beta_idx_2a_exp_basic]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_2a_wei_basic  <- grepl("Beta_SE", colnames(result2a_weibull_basic$param.samples)) # use to get beta estimates/samples
eta_2a_wei_basic <- exposure_model_2$X %*% t(result2a_weibull_basic$param.samples[,beta_idx_2a_wei_basic]) # get intensity matrix/time series (X(se) x Beta(se))
 
 plot(apply(eta_2a_exp_SMC, 1, mean), 
      type = 'l', 
      col="blue",
      main = 'Model 2a Intensity Prediction',
      ylab = 'Intensity (Eta)',
      xlab = 'Epidemic Day',
      ylim = c(-15, max(eta_2a_exp_SMC,eta_2a_wei_SMC,eta_2a_exp_basic,eta_2a_wei_basic)*1.5))
 lines(apply(eta_2a_wei_SMC, 1, mean), lty = 1, col = "red")
 lines(apply(eta_2a_exp_basic, 1, mean), lty = 1, col = "chartreuse2")
 lines(apply(eta_2a_wei_basic, 1, mean), lty = 1, col = "darkgoldenrod1")
 abline(v=c(184,368), lty=c(2,2), lwd=c(2, 2), col="black")

 
 
 
 legend("bottomleft", legend = c("Exponential (SMC)", "Weibull (SMC)",
                               "Exponential (Basic)", "Weibull (Basic)"), 
         lty = c(1,1,1,1), col = c("blue", "red", "chartreuse2", "darkgoldenrod1"))


# alabama has least epidemic intensity (which is true considering the amount of cases compared to fl and georgia), followed by florida and georgia
```

```{r}
beta_idx_3_exp  <- grepl("Beta_SE", colnames(result4$param.samples)) # use to get beta estimates/samples
eta_3_exp <- exposure_model_4$X %*% t(result4$param.samples[,beta_idx_3_exp]) # get intensity matrix/time series (X(se) x Beta(se))

beta_idx_3_wei <- grepl("Beta_SE", colnames(result6$param.samples)) # use to get beta estimates/samples
eta_3_wei <- exposure_model_4$X %*% t(result6$param.samples[,beta_idx_3_wei]) # get intensity matrix/time series (X(se) x Beta(se))

 
 plot(apply(eta_3_exp, 1, mean), 
      type = 'l', 
      col="blue",
      main = 'Model 3 Intensity Prediction',
      ylab = 'Intensity (Eta)',
      xlab = 'Epidemic Day',
      ylim = c(-15, 7))
 lines(apply(eta_3_wei, 1, mean), lty = 1, col = "chartreuse2")
 abline(v=c(450,900), lty=c(2,2), lwd=c(2, 2), col="black")

 
 
 
 legend("bottomleft", legend = c("Exponential (SMC)", "Weibull (SMC)"), 
         lty = c(1,1), col = c("blue", "chartreuse2"))


# alabama has least epidemic intensity (which is true considering the amount of cases compared to fl and georgia), followed by florida and georgia
```

# Model 1a (Exp)

```{r}
summary(result1a)
```

# Model 1a (Weibull)

```{r}
summary(result1a_weibull)
```

# Model 2a

```{r}
summary(result2b)
```

# Model 2a (Weibull Distribution)

```{r}
summary(result2a_weibull)
```

# Model 3 (Exponential)

```{r}
summary(result4)
```

# Model 3 (Weibull)

```{r}
summary(result6)
```


# Bayes Factor (Model 1a vs Model 1b vs Model 1c)

```{r}
print(comps)
# model 1a best
```

# Bayes Factor (Model 2a vs Model 2b vs Model 2c)

```{r}
print(comps_1)
# model 2a best
```

# Bayes Factor (Exponential vs Weibull under Model 1a)

```{r}
print(comps_2)
# exponential better
```

# Bayes Factor (Exponential vs Weibull under Model 2a)

```{r}
print(comps_3)
# weibull better
```

# Runtimes

```{r}

print(timeMatrix[,1:3])

# save data with best results...clear workspace and rerun for runtimes...delete everything besides time matrix and load it into the saved workspace
```
